Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-08 exp1/present2013.tex
randomization
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@656 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

>>>>

\section{Discussion}

\begin{frame}{Linearity and choice of levels}
  \begin{itemize}
  \item 2-level experiments can only model linear effects.
  \item Choice of levels may be critical.
  \item If response is known to be non-linear, using more levels must be considered.
  \end{itemize}

\end{frame}
\note{2-level good enough for identifying effects, insufficient as
  statistical model}

\begin{frame}{The role of randomization}
  \begin{itemize}
  \item We have allowed us to disregard the effect of caching,
    warm-up-runs, etc.
  \item This is different from neutralizing the effect!
  \item They are now ``lurking variables''.
  \item They contribute to the overall unexplained variance.
  \item Unexplained variance should be kept to a minimum.
  \item Time-dependent or order-dependent factors may be required.
  \end{itemize}
\end{frame}
\note{Even though we know caching is important}
\note{Caching is good practice, shouldn't be neutralized. Warm-up may
  not be permissible in real-time scenarios}
\note{Variance can obscure problems like ``Implement:TripleC''}
\note{most problematic cases are those that are
covered neither by the broad factors, nor the lurking variables, or
any of the specific factors. Invalidated by absence of language
features, such as solution modifiers.}

\section{Future Work}

@@

\begin{frame}{Rules of Thumb}

\begin{enumerate}
\item Are there factors that cover all realistic features?
\item If not, are they adequately covered by randomization?
\item If so, would the variance resulting from randomization obscure
  factors that could provide clues that the levels are wrongly set?
\item By carefully examining interactions with ``Implement'', are
  there any that are unaccounted for, and that could point out wrongly
  set levels?
\end{enumerate}
